---
title: "Cryptocurrency Indicators"
author: "Aimé OKOKO"
date: "`r paste('Yahoo finance data retrieved on', Sys.Date())`"
runtime: shiny
output: 
  html_document: 
    keep_md: yes
    # theme: darkly
---

This application uses updated Yahoo finance data to compute the Relative Strength Index of a set of Cryptocurrencies. 
Relative Strength Index is computed by the formula : 

\begin{equation}

RSI = 100 - [\frac{100}{1 + 
\frac{Average \ gain}{Average \ loss}
} ]

\end{equation}

The user can choose the cryptocurrency of interest and see how the price and the RSI evolve over time. He can also drag on the plot to choose a period of interest.

The table below shows today's RSI value.

**Ps : This app is just for illustrative purpose**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, eval = T)
```


```{r libraries}
library(dygraphs)
library(dplyr)
library(TTR)
library(quantmod)
library(stringr)
library(purrr)
```

## Cryptocurrency

```{r}
options("getSymbols.warning4.0"=FALSE)
symb <- c("BTC-USD", "ETH-USD")
crypt_nam <- str_sub(symb, 1, -5)

data_list <- lapply(symb, function(x){ 
  getSymbols(x)
  get(x)})
```


```{r calcul_indicateurs, cache=T}

TA <- matrix(data = 0, nrow = 1, ncol = 1) #TA for technical analysis 
TA <- as.data.frame(TA)
names(TA) <- "rsi"

mes_crypt <- list()

for (i in seq_along(data_list)){
  data <- data_list[[i]]
  data <- na.omit(data) #Suppression de valeurs manquantes
  names(data) <- c("open","high","low","close",
                   "volume","adjusted")
  
    data$rsi <- RSI(Cl(data))
    
    bband <- BBands(HLC(data))
  
  data <- cbind(data, bband)
  mes_crypt[[i]] <- data
  TA[i,] <- data[nrow(data), 7]

}

names(mes_crypt) <- crypt_nam #Nommage de la liste

TA <- sapply(TA, function(x) round(x, 2)) %>% 
  as.data.frame()
TA$name <- crypt_nam
TA$order <- 1:nrow(TA)
```


```{r data, cache=T}
# Relative Strength Index (30-70)
f_rsi <- function(){
  renderDygraph({
  ma_crypto <- input$coin

data <- mes_crypt[[ma_crypto]]
  
  dygraph(data[,"rsi"], main = "RSI", group = "stock",
        height=100,width=700) %>%
  dyLegend(show="follow") %>%
  dyLimit(limit = 80,
          label = "Overbought",
          labelLoc = "left",
          color = "red",
          strokePattern = "dotted") %>%
  dyLimit(limit = 40,
          label = "Oversold",
          labelLoc = "left",
          color = "red",
          strokePattern = "dotted")
    })
  }

```


```{r indicateurs, echo=F, cache=F}


selectInput("coin", "Choose coin", choices = crypt_nam,
            selected = "BTC")

renderDygraph({
ma_crypto <- input$coin

data <- mes_crypt[[ma_crypto]]
candle <- OHLC(data)

 dygraph(candle, main = ma_crypto, group = "stock", width = 650, height = 300) %>%
  dyCandlestick() %>%
  dyLegend(show = "follow")

})
#RSI
f_rsi()

```
```{r table}

#Table d'indiacateurs et de cryptos pour la journée

#Indicateurs

DT::datatable(TA[,c("order", "name", "rsi")],
              caption = "Today's RSI",
              rownames = F,
              filter = 'top',
              width = 1000,
              options = list(
  pageLength = 100
))
```


